---
title: "Learning about Assay Data in Bioconductor"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(SummarizedExperiment)
```


## Learning Objectives

- *Learn about* the structure of a common Bioconductor Object, `SummarizedExperiment`
- *Learn about* slots in Bioconductor Objects
- *Learn about* the `colData` slot in a `SummarizedExperiment`
- *Learn about* the `assay` slot
- *Subset and query* data by using `colData` and `assayData` together
- *Visualize* an `SummarizedExperiment` object

### Welcome to Bioconductor!

What is Bioconductor? 

Bioconductor is a set of R Packages that is made for high-throughput bioinformatics analysis. 

What makes Bioconductor so powerful is that these packages share data structures called *objects*. 

However, understanding how these *objects* work can be a real barrier to getting started in Bioconductor. 


### Installing Bioconductor

Part of what makes Bioconductor so confusing to install is that it has its own installer, which lives in a package called `BiocManager`. So, the first step to install Bioconductor packages is to use `BiocManager::install()`.

We're going to install the `SummarizedExperiment` package and the `airway` dataset.

```
install.packages("BiocManager")
BiocManager::install(c("SummarizedExperiment", "airway"))

```

### Walk Before We Can Run

You might be impatient to load your data into Bioconductor. 

We should learn about how the objects work before we try to load our data. 

Let's take a guided tour of a commponly used object in Bioconductor called `SummarizedExperiment`. 

To do so, we need to load the `SummarizedExperiment` package, and the `airway` dataset.

```{r}
library(SummarizedExperiment)
library(airway)
data(airway)
```

### Reading the print output of SummarizedExperiment


```{r}
airway
```

### Access sample metadata using `colData`

```{r}
colData(airway)
```


### assays()



```{r}
assays(airway)
```
So, there's an object called `count`.

```{r}
head(assays(airway)$counts)
```
### Check Yourself

What do the rows and columns correspond to in this matrix?



### rowData

```{r}
rowInfo <- rowRanges(airway)

names(rowInfo)[1]

rowInfo[1]

slotNames(rowInfo[1])
```


### Subsetting Data to Specific Samples



### Exercise


